### 2011-05-13 paper/paper.tex
connectedness stuff

It is also shown in \cite{Smith} that the distributions from a Markov chain with a symmetric transition function eventually \emph{converge} to this stationary uniform distribution, which shows that these algorithms for sampling uniformly will work, given enough time. The \emph{mixing time} of an algorithm is the number of iterations required for the distribution to converge to the uniform distribution within some desired precision. Ideally, we want the mixing time to be small. However, in the next section, we will see that this can take a very long time to mix, and we modify the algorithm in an attempt to fix this problem.

>>>>

It is also shown in \cite{Smith} that the distributions from a Markov chain with a symmetric transition function eventually \emph{converge} to this stationary uniform distribution, provided that the probability distribution is nonzero everywhere. This is true for all of the methods we want to use except ball-walking. However, since our convex region $\mathcal{R}$ is connected, the distribution is positive everywhere if we consider our transition function to be the composition of sufficiently many steps. If the distribution for each $k^\text{th}$ step converge to the uniform distribution, for some $k$, then all the distributions will converge to the uniform distribution, since we can always apply the same argument, but shifted.

This shows that these algorithms for sampling uniformly will work, given enough time. The \emph{mixing time} of an algorithm is the number of iterations required for the distribution to converge to the uniform distribution within some desired precision. Ideally, we want the mixing time to be small. However, in the next section, we will see that this can take a very long time to mix, and we modify the algorithm in an attempt to fix this problem.
